Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-04 draft/accordionComplexSurfaces.tex
reorder examples
Structure of proof of finiteness of faces, bis.

\begin{remark}
The following observations are useful for the computation of examples.
\begin{itemize}
\item The set~$V_{\bar Q}$ has one vertex for each straight walk in~$\bar Q$ (equivalently, for each maximal path in~$\bar Q$).
      Finite straight walks yield vertices on the boundary, while infinite cyclic straight walks yield punctures.
\item The dissection~$\dissection_{\bar Q}$ has one arc for each vertex~$p \in \bar Q_0$, obtained by concataining the sides~$\Enrt{\alpha} = \Enrs{\beta}$ and~$\Enrt{\alpha'} = \Enrs{\beta'}$ where~$p = t(\alpha) = s(\beta) = t(\alpha') = s(\beta')$, $\alpha\beta \notin I$ and~$\alpha'\beta' \notin I$.
\item The dissection~$\dissection_{\bar Q}$ has one $\ell$-cell for each straight walk of length~$\ell$ in~$\bar Q\koszul$.
\item The number of boundray components of~$\surface(\bar Q)$ can be computed as follows.
      There are two natural perfect matchings whose vertices are the blossoming vertices of~$\bar Q$: one is obtained by putting an edge between two vertices~$v_1$ and~$v_2$ whenever there is a straight walk of~$\bar Q$ relating them, and the other is obtained by doing the same for~$\bar Q \koszul$.
      Let~$G$ be the superposition of these two perfect matchings.
      Then the number of boundary components of~$\surface(\bar Q)$ is the number of connected components of~$G$.
\item The genus of the surface~$\surface(\bar Q)$ is
      \[
       g = \frac{|Q_1| - |Q_0| - b + 2}{2},
      \]
      where~$b$ is the number of boundary components (see above for a way to compute~$b$).
      Indeed, ~$g=\frac{2-\chi(\surface(\bar Q))}{2}$, where~$\chi(\surface(\bar Q))$ is the Euler characteristic of~$\surface(\bar Q)$.
      The dissection~$\dissection$ provides a cellular decomposition of~$\surface(\bar Q)$ on which we fill the boundary components with disks.  
      The number of faces of this cellular decomposition is~$b$, its number of edges is~$|Q_0|$ and its number of vertices is the number of finite straight walks in~$\bar Q$, which is equal to~$2|Q_0| - |Q_1|$.
      The above formula for~$g$ follows.

\end{itemize}
A similar remark holds dually for~${V_{\bar Q}}\dual$ and~${\dissection_{\bar Q}}\dual$.
\end{remark}

@@

@@

\begin{lemma}
\label{lemm:facesAreBounded}
There is a bound on the number of elements of a finite face of~$\NKC$.
\end{lemma}

\begin{lemma}
\label{lemm:facetsAreFinite}
Any face of~$\NKC$ and~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ is contained in a finite maximal face.
\end{lemma}
\begin{proof}
 We provide two proofs of the lemma.  One is combinatorial and applies to~$\NKC$, and the other is geometric and applies to~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$.

 {\it Combinatorial proof.}
 This is an immediate consequence of Lemma \ref{lemm:facesAreBounded}.

@@

>>>>

\begin{remark}
The following observations are useful for the computation of examples.
\begin{itemize}
\item The set~$V_{\bar Q}$ has one vertex for each straight walk in~$\bar Q$ (equivalently, for each maximal path in~$\bar Q$).
      Finite straight walks yield vertices on the boundary, while infinite cyclic straight walks yield punctures.
\item The dissection~$\dissection_{\bar Q}$ has one arc for each vertex~$p \in \bar Q_0$, obtained by concataining the sides~$\Enrt{\alpha} = \Enrs{\beta}$ and~$\Enrt{\alpha'} = \Enrs{\beta'}$ where~$p = t(\alpha) = s(\beta) = t(\alpha') = s(\beta')$, $\alpha\beta \notin I$ and~$\alpha'\beta' \notin I$.
\item The dissection~$\dissection_{\bar Q}$ has one $\ell$-cell for each straight walk of length~$\ell$ in~$\bar Q\koszul$.
\item The number of boundary components of~$\surface(\bar Q)$ can be computed as follows.
      There are two natural perfect matchings whose vertices are the blossoming vertices of~$\bar Q$: one is obtained by putting an edge between two vertices~$v_1$ and~$v_2$ whenever there is a straight walk of~$\bar Q$ relating them, and the other is obtained by doing the same for~$\bar Q \koszul$.
      Let~$G$ be the superposition of these two perfect matchings.
      Then the number of boundary components of~$\surface(\bar Q)$ is the number of connected components of~$G$.
\item The genus of the surface~$\surface(\bar Q)$ is
      \[
       g = \frac{|Q_1| - |Q_0| - b + 2}{2},
      \]
      where~$b$ is the number of boundary components (see above for a way to compute~$b$).
      Indeed, ~$g=\frac{2-\chi(\surface(\bar Q))}{2}$, where~$\chi(\surface(\bar Q))$ is the Euler characteristic of~$\surface(\bar Q)$.
      The dissection~$\dissection$ provides a cellular decomposition of~$\surface(\bar Q)$ on which we fill the boundary components with disks.  
      The number of faces of this cellular decomposition is~$b$, its number of edges is~$|Q_0|$ and its number of vertices is the number of finite straight walks in~$\bar Q$, which is equal to~$2|Q_0| - |Q_1|$.
      The above formula for~$g$ follows.
\end{itemize}
A similar remark holds dually for~${V_{\bar Q}}\dual$ and~${\dissection_{\bar Q}}\dual$.
\end{remark}

@@

\begin{example}[Reversed paths]
\label{exm:doublePath}
Consider the following family of locally gentle quivers:
\vincent{TODO double path}
\end{example}

@@

\begin{lemma}
\label{lemm:facesAreBounded}
There is a bound on the number of elements of a finite face of~$\NKC$.
\end{lemma}
\begin{proof}
 We provide two proofs of the lemma.  One is combinatorial and applies to~$\NKC$, and the other is geometric and applies to~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$.

@@

\begin{lemma}
\label{lemm:facetsAreFinite}
Any face of~$\NKC$ and~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ is contained in a finite maximal face.
\end{lemma}
\begin{proof}
 This is an immediate consequence of Lemma \ref{lemm:facesAreBounded}.
\end{proof}
